Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs

### 2020-05-15 manuscript/manuscript.tex
Before pass the ball to Tommaso

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mass relations by lensed AGN hosts]{Testing the evolution of the correlations between Supermassive Black Holes and Their Host Galaxies using Eight Strongly Lensed AGNs.}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
Tommaso Treu$^{1}$,
Simon Birrer$^{2}$,
Dominique Sluse$^{3}$,\newauthor
Chris Fassnacht$^{4}$,
Matthew W. Auger$^{5}$,
Kenneth C. Wong$^{6}$,
Sherry H. Suyu$^{7,8,9}$,\newauthor
Takahiro Morshita$^{10}$,
and et al.
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{4}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{5}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{6}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{7}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{8}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{9}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{10}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
$^{11}$TBC
}

@@

% Abstract of the paper
\begin{abstract}
Strong lensed active galactic nuclei (AGN) has been considered as a unique tool to exam the correlations between the mass of the supermassive Black Hole and its host galaxies. In this work, we have adopted eight strongly lensed system from our collaboration. The deep {\it Hubble Space Telescope}(\hst) data and adopt the \lenstronomy\ to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on the assumed stellar population. 
The \mbh\ are estimated using the board emission line. We compare our inference to the ones in the literature and find a consistent result. The consistent scaling resolutions derived from our sample confirm the evolution conclusion and confirm the the power of using strong lensed AGNs. The number of the detection of the lensed AGNs are supposed to increase rapidly leave this topic with a bright future...
\end{abstract}

@@

A powerful way to understand the origin of the correlations is to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}. Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging. Combining the new sample with published samples in both local and intermediate redshift range, they strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy. With the goal of testing theoretial ideas, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}. The observed tightness of the  scaling relations at high-$z$ is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature. 
%, a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.

Benefiting from the gravitational lensing magnification and stretching effect, strong lensed AGNs have been used as unique tool to make progress in study the scaling relations at the distance universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived. Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} has carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration. This work confirms that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. With a following up effort, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.

In this work, we intend to make progress by deriving the measurements of the \mbh-\mstar\ relation using the entire eight systems as introduced in \citet{Ding2017a}. We develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to assure the accuracy of our measurements. We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check. To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets. Besides, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample. The extended range of the eight systems would help us to make a direct comparison to the latest measurements by D20.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data condition and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach that designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with contrast sample to study the evolution in Section~\ref{sec:result}. The discussion and conclusions are drawed in Section~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the entire sample consistently.

@@

Based on the observational data of these eight systems, \citet{Ding2017a} performed the extensive and realistic simulation exercise using the \hst\ image data of these eight systems and confirm that the source reconstruction using the state-of-the-art modelling technique is trustworthy. % when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. 
Here, we re-summarized the imaging data information and listed in Table~\ref{data_set}. Besides the image data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As will show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to estimate their accurate \mstar.

While we note that the sample size by this work (i.e., eight systems) is limited. Rather than using our measurement to constrain the evolution of the scaling relation, we plan to use our data and make a direct comparison to the recent efforts in D20, which includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

\begin{table*}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN observational details.}\label{data_set}
\resizebox{13cm}{!}{
     \begin{tabular}{cccccccc}
        \hline
Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale \\
 & & & & time (s) &&& (drizzled) \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ \\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ \\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ \\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$ \\
HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is also presented in~\citet{Ding2017a}. 
      \item $^a$: For HS2209, it is visited by \hst\ twice ({\it vis05} and {\it vis06}). The exposure time is thus given separately.
\end{tablenotes}  
%\end{threeparttable}
\end{table*}

To assure the consistency of the \mbh\ between the usage of different board lines, we adopt a class of self-consistent recipes to estimate the \mbh. For the entire AGN systems, we follow D20 and adopt the following virial formalism:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The board line information of our samples are adopted from the literature \citep{Sluse2012, Peng2006, Shen2011}. The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}. The uncertainty of the \mbh\ are expected as $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates.}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{ccccc}
        \hline
Object ID & Line(s) used & FWHM & log($L_\lambda$) & $\log$\mbh \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 \\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 \\
SDSS1206 & \Mgii & 5632 & 45.61$^a$ & 8.88 \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 \\
HS2209 & \Mgii & 3245 & 45.71 & 8.75 \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The reference for the board line information. For HS2209, its board line is estimated in this work using the same approach as~\citet{Sluse2012}.\\
$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect.
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
We perform the study of the lens modelling to reconstruct the photometry of the lensed host galaxies in this section. Our lens systems are a part of the H0LiCOW project, and the lens models of 4/8 systems, including HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been derived. Aiming at the strong lensing time-delay cosmography~\citep{Treu2016}, these works mainly focused on deriving the precise and accurate lens models, while the reconstruction of the reconstructed host galaxies from these works can be considered as a by-product. In this work, we apply the state-of-the-art lens modelling technique and perform an independent effort focusing on recovering the photometry of the host galaxy. As will show, our approach would allow us to obtain a one-step host magnitude as defined by \sersic\ surface brightness profile; thus the measurements of the host galaxy properties would be more consistent to the ones in the literature. For the 4/8 systems which has been studied in H0LiCOW project, we will make comparison to understand the accuracy of our analysis.

\subsection{Data Preparation and Modelling Setup}
We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}. We then adopt the {\sc photutils} by Python to model the global background light in 2-D based on SExtractor algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.

We carry out the forward modelling process to constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy, simultaneously. For any extended objects including the lensing galaxy and source galaxy, we assume their photometry can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical inference\footnote{It has been studied in~\citet{Ding2017a} that setting \sersic\ $n$ as this prior value would result in a consistent host magnitude inference compared to a prior with fixing $n$ to the truth.}. The bright nuclei is unsolved and modelled by a scaled point spread function (PSF). We also jointly fit the AGN position to the center of its host galaxy. We adopt the elliptical Power-law model to define the surface mass density of the deflector; an external shear component is also added.

We employ the imaging modelling tool \lenstronomy~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system. The distribution of the fitting inference by the overall choices are supposed to sufficiently cover the truth. We then apply a statistical measurement and perform weighting algorithm to derive the final inference and estimate the uncertainty level. The different modelling choices are selected based on the following options:
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF to input to the fitting.
\item The central pixel of the AGNs are very bright and have systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, the different relative level to the pixel sizes is selected, including [$2\times2$, $3\times3$] pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we fix it with three optional values $[1.9, 2.0, 2.1]$.
\end{enumerate}

In general, for one lens system with a number of $N$ initial PSFs, we select in total of $N\times12$ (i.e., $2 \times2 \times3$) different choices of fitting. After all sets of fittings completed, we rank their performance of each choice based on their best-fitted $\chi^2$ value. Since there is no evidence of an better performance for the options between {\it noise boost} and {\it PSF iteration}, we selected the top-4 fittings from both of them and then combining their best-fit results based on the weighting algorithm introduced by D20. The weights are defined by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter\footnote{Defining $\alpha$ as the {\it inflation} parameter literally means that it has to be larger than~$1$. If $\alpha<1$, introducing the $\alpha$ would have a side-effect because the relative likelihood between different the selected choices would be too close.} so that when $i=4$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=4} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2.
\end{eqnarray}

>>>>

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[Mass relations by lensed AGN hosts]{Testing the Evolution of the Correlations between Supermassive Black Holes and their Host Galaxies using Eight Strongly Lensed AGNs}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[X. Ding et al.]{
Xuheng Ding$^{1}$\thanks{E-mail: dxh@astro.ucla.edu},
Tommaso Treu$^{1}$,
Simon Birrer$^{2}$,
Adriano Agnello$^{3}$,\newauthor
Dominique Sluse$^{4}$,
Chris Fassnacht$^{5}$,
Matthew W. Auger$^{6}$,
Kenneth C. Wong$^{7}$, \newauthor
Sherry H. Suyu$^{8,9,10}$,
Takahiro Morshita$^{11}$,
and et al.
\\
\\
% List of institutions
$^{1}$Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA\\
$^{2}$Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{3}$European Southern Observatory, Karl-Schwarzschild-Strasse 2, 85748 Garching, Germany\\
$^{4}$STAR Institute, Quartier Agora - All\'ee du six Ao\^ut, 19c B-4000 Li\`ege, Belgium\\
$^{5}$Department of Physics, University of California, Davis, CA 95616, USA\\
$^{6}$Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK\\
$^{7}$Kavli IPMU (WPI), UTIAS, The University of Tokyo, Kashiwa, Chiba 277-8583, Japan\\
$^{8}$Max-Planck-Institut f{\"u}r Astrophysik, Karl-Schwarzschild-Str.~1, 85748 Garching, Germany\\
$^{9}$Physik-Department, Technische Universit\"at M\"unchen, James-Franck-Stra\ss{}e~1, 85748 Garching, Germany\\
$^{10}$Academia Sinica Institute of Astronomy and Astrophysics (ASIAA), 11F of ASMAB, No.1, Section 4, Roosevelt Road, Taipei 10617, Taiwan\\
$^{11}$Space Telescope Science Institute, 3700 San Martin Drive, Baltimore, MD 21218, USA
$^{11}$TBC
}

@@

% Abstract of the paper
\begin{abstract}
  One of the main challenges in using high redshift active galactic nuclei to study the correlations between the mass of the supermassive Black Hole (\mbh) and the properties of their active host galaxies is instrumental resolution. The magnification of strongly lensed quasars provide a way to effectively increase instrumental resolution and thus overcome this challenge. In this work, we study eight strong lens systems with deep {\it Hubble Space Telescope}(\hst) imaging, using the state-of-the-art \lenstronomy\ code to reconstruct the image of the source. Using the reconstructed brightness of the host galaxy, we infer the host galaxy stellar mass based on stellar population models. 
  \mbh\ are estimated from broad emission line using standard methods. Our results are in good agreement with recent work based on non-lensed AGN, providing additional evidence that the correlation evolve over cosmic time.  At the moment, the \pink{sample size of lensed AGN is small and thus} provide mostly a consistency check on systematic errors related to resolution for the non-lensed AGN. However, the number of known lensed AGN is expected to increase dramatically in the next few years, through dedicated searches in ground and space based wide field surveys, and may become a key diagnostic of black hole and galaxy co-evolution. 
\end{abstract}

@@

A powerful way to understand the origin of the correlations is to study them as a function of redshift, determining how and when they emerge and evolve over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13,Sun2015, Park15}. Recently, based on a sample of 32 X-ray-selected type-1 AGNs in deep survey fields, \citet{Ding2020a} (hereafter, D20) measured the scaling relations in the redshift range $1.2<z<1.7$ using multi-color Wide Field Camera 3 (WFC3) \hst\ imaging. Combining the new sample with published samples in both local and intermediate redshift range, D20 strengthen the support for an evolution scenario in which the growth of BHs evolution predates that of  the bulge component of the host galaxy. In a follow-up paper, \citet{Ding2020b} compared the D20 measurements to the predictions by the numerical simulations including the hydrodynamic simulation MassiveBlackII~\citep{Khandai2015} and a semi-analytic model~\citep{Menci2014}. The observed tightness of the  scaling relations at high-$z$ is consistent with the hypothesis that AGN feedback drives the scaling correlations, and disfavors the hypothesis of the correlations being purely stochastic in nature. 
% , a larger sample at the higher redshift range would be useful to increase the resolution of the evolution and confirm these hypothesises.

As the samples of AGN grow to increase statistical power, it is very important to make sure that systematics do not dominate the error budget. One of the main potential source of systematics is the finite resolution of \hst\ images. Even with state of the art techniques, AGN hosts remain barely resolved at \hst\ resolution, and therefore it would be very useful to verify the results at higher resolution. This is the goal of this work.

It has been long recognized that lensed AGNs, by virtue of magnification, can provide unique insights inro the scaling relations the distant universe~\citep{Peng2006}, provided that the lens modelling could be accurately derived. Aiming at verifying the fidelity of the modern lens modelling technique, \citet{Ding2017a} carried out extensive and realistic simulations tests based on the deep \hst\ observations for a sample of eight lens systems in the \hc\ Lenses in COSMOGRAIL's Wellspring (H0LiCOW, PI: Suyu) collaboration. They confirm that the reconstruction of the lensed host galaxy properties can be recovered with better precision and accuracy than the typical \mbh\ uncertainty. Then, \citet{Ding2017b} applied the advanced techniques to two strongly lensed systems analyzed by the H0LiCOW collaboration~\citep{Suyu2013, Wong2017} to study their \mbh-\lhost\ relations and obtained consistent scaling relations compared with the samples from the literature.

In this work, we expand the measurements of the \mbh-\mstar\ relation using the full sample of eight lensed AGN introduced by \citet{Ding2017a}.  In order to take advantage of the excellent quality of the data, we develop an independent approach to achieve a one-step inference of the host galaxy photometry from the eight lensed AGNs. We adopt a set of extended modelling choices to assure the accuracy of our measurements. We compare the inference of our new measurements to the ones which have been modelled by the H0LiCOW collaboration to make the cross-check. To assess an accurate inference of stellar mass, we utilize the imaging data taken with the \hst\ multi-band filter to obtain the color information for 3/8 of our targets. Furthermore, we adopt a class of self-consistent recipes to recalibrate the \mbh\ of our sample, in a manner consistent with D20. Given the similar redshift range, the high data quality, and consistent state of the art techniques, this sample of lensed AGN provides an excellent verfication of the D20 results.

This paper is structured as follows. In Section~\ref{sec:sample_select}, we introduce the sample including their imaging data and the BH masses. In Section~\ref{sec:lens_model}, we describe our approach designed to infer the lens models and reconstruct the host galaxy. We use the inferred photometry to derive the stellar mass and the scaling relations and combine with D20 sample to study the evolution in Section~\ref{sec:result}. Discussion and conclusions are drawn in Section~\ref{sec:diss} and~\ref{sec:con}. Throughout this paper, we adopt a standard concordance cosmology with parameters adopted as $H_0= 70$ km s$^{-1}$ Mpc$^{-1}$, $\Omega{_m} = 0.30$, and $\Omega{_\Lambda} = 0.70$. Magnitudes are presented in the AB system. A Chabrier initial mass function (IMF) is employed for the sample, consistently with D20.

@@

Based on the observational data of these eight systems, \citet{Ding2017a} performed the extensive and realistic simulation exercise using the \hst\ image data of these eight systems and confirm that the source reconstruction using the state-of-the-art modelling technique is trustworthy. % when its magnitude are brighter than 20 magnitude, 2$-$4 magnitudes dimmer than the AGN. 
Here, we re-summarized the imaging data information and listed in Table~\ref{data_set}. Besides the image data shown in this table, we also analyzed the multi-band \hst\ imaging data to derive the host color information for 3/8 systems. As we show in Section~\ref{sec:mstar}, we use the color information to fit for the best stellar population to improve the accuracy of the estimate of \mstar.

The sample of lensed AGN is too limited in size to constrain evolution by itself. Therefore, we use it primarily to verify the results of D20.  The D20 sample includes 32 AGN measurements at redshift range $1.2<z<1.9$, 59 collected intermediate redshift AGN measurements~\citep{Bennert11, SS13, Cisternas2011} and 55 collected local measurements~\citep{Bennert++2011, H+R04}. It is worth noting that they are so far the largest \hst\ imaging AGN sample with redshift range up to $z\sim1.9$.

\begin{table*}
\centering
%\begin{threeparttable}
\caption{Summary of lensed AGN observational details.}\label{data_set}
\resizebox{13cm}{!}{
     \begin{tabular}{cccccccc}
        \hline
Object ID & $z$ & camera & Filter & exposure & Program ID & PI & pixel scale \\
 & & & & time (s) &&& (drizzled) \\ \hline
HE0435$-$1223 & 1.69 & WFC3-IR & F160W & 9340 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
RXJ1131$-$1231 & 0.65 & ACS & F814W & 1980 & 9744 & C.S. Kochanek & $0\farcs{}05$ \\
WFI2033$-$4723 & 1.66 & WFC3-IR & F160W & 26257 & 12889 & S. H. Suyu & $0\farcs{}08$ \\
SDSS1206$+$4332 & 1.79 & WFC3-IR & F160W & 8457 & 14254 & T. Treu & $0\farcs{}08$ \\
HE1104$-$1805 & 2.32 & WFC3-IR & F160W & 14698 & 12889 & S. H. Suyu  & $0\farcs{}08$ \\
SDSS0246$-$0825 & 1.68 & WFC3-UVIS & F814W & 8481 & 14254 & T. Treu & $0\farcs{}03$ \\
HS2209$+$1914$^a$  & 1.07 & WFC3-UVIS & F814W & 9696 + 4542 & 14254 & T. Treu & $0\farcs{}03$ \\
HE0047$-$1756 & 1.66 & WFC3-UVIS & F814W & 9712 & 14254 & T. Treu & $0\farcs{}03$ \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
      \small
      \item Note: $-$ The observational information is also given by~\citet{Ding2017a}. 
      \item $^a$: HS2209, was visited by \hst\ twice ({\it vis05} and {\it vis06}) at different orientations. The exposure time is thus given separately.
\end{tablenotes}  
%\end{threeparttable}
\end{table*}

To ensure the consistency of \mbh\ estimates based on different broad lines, we adopt a the following set of self-consistent recipes following D20:
\begin{eqnarray}
\label{recipe}
\log \left(\frac{\mathcal M_{\rm BH}}{M_{\odot}}\right)&~=~& a+b \log \left(\frac{ \rm L _{\lambda_{line}}}{10^{44}{\rm erg~s^{-1}}}\right) \nonumber\\
&~+~& 2 \log \left(\frac{\rm FWHM(line)}{1000 ~{\rm km~s^{-1}}}\right) , 
\end {eqnarray}
%
with $a$\{\Civ, \Mgii, \Hb\}=\{6.322, 6.623, 6.910\},
$b$\{\Civ, \Mgii, \Hb\}=\{0.53, 0.47, 0.50\},
$\lambda_{line}$\{\Civ, \Mgii, \Hb\}=\{1350, 3000, 5100\}.
%
The broad line properties of our samples are \pink{mostly} adopted from the literature. % \citep{Sluse2012, Peng2006, Shen2011}.
\pink{For SDSS1206, the line properties have been inferred by~\citet{Shen2011}. However, this system was investigated as a non-lensed AGN and the lensing magnification on the intrinsic continuum luminosity was not considered. We follow~\citet{Birrer2019} and apply the same magnification correction on the $\log(L_\lambda)$ in this work. For the rest of the lens sample except HS2209, their broad line properties are adopted from the literatures~\citep{Sluse2012, Peng2006} with lensing magnification effect considered. For HS2209, the spectrum data was observed from ESI in September 2015. We derived the line properties using the same approach as~\citep{Sluse2012}. \todo{Dominique and Chris can give more details here.} }. The \mbh\ measurements, together with the properties of the board-line are listed in Table~\ref{mbh}. 
The uncertainty of the \mbh\ are estimated to be $0.4$~dex.

\begin{table}
\centering
%\begin{threeparttable}
\caption{Summary of \mbh\ estimates, \pink{based on equation~\eqref{recipe}.}}\label{mbh}
\resizebox{8.5cm}{!}{
     \begin{tabular}{cccccc}
        \hline
Object ID & Line(s) & FWHM & log($L_\lambda$) & $\log$\mbh & ref.  \\
& & (\kms) & (${\rm erg~s^{-1}}$) & (M$_{\odot}$) \\ \hline
HE0435 & \Mgii & 4930 & 45.14 & 8.54 & (1) \\
RXJ1131 & \Mgii/\Hb & 5630/4545 & 44.29/44.02 & 8.26/8.23 & (1)\\
WFI2033 & \Mgii & 3960 & 45.19 & 8.38 & (1) \\
SDSS1206 & \Mgii & 5632 & 45.01 & 8.77 & (2) \\
HE1104 & \Civ & 6004 & 46.18 & 9.03 & (3) \\
SDSS0246 & \Mgii & 3700 & 45.19 & 8.32 & (1) \\
HS2209 & \Mgii & 3245 & 45.71 & 8.75 & \pink{here}  \\
HE0047 & \Mgii & 4145 & 45.59 & 8.60 & (1) \\
        \hline
     \end{tabular}
    }
\begin{tablenotes}
\small
\item Note: $-$ The broad line properties.\\ %For HS2209, the properties are derived in this work using the same approach as~\citet{Sluse2012}.
\pink{Reference: (1)~\citet{Sluse2012}, (2)~\citet{Shen2011}, (3)~\citet{Peng2006}.}\\
%$^a$: For SDSS1206, we follow~\citet{Birrer2019} and correct the AGN continuum luminosity $\log(L_\lambda$) by taking account the magnification effect {\bf [TT: how about the others?].}
\end{tablenotes}  
%\end{threeparttable}
\end{table}

\section{surface photometry inference}\label{sec:lens_model}
%
In this section, we describe how we derived surface photometry of the lensed galaxies taking lensing effects into account. Lens models of 4/8 systems, namely HE0435~\citep{Wong2017}, RXJ1131~\citep{Suyu2013}, WFI2033~\citep{Rusu2019} and SDSS1206~\citep{Birrer2019} have been published by the H0LiCOW project. The goal of those models was strong lens time-delay cosmography~\citep{Treu2016}, and the reconstruction of the host galaxy light (pixelized or via shapelets) was a byproduct. \citet{Ding2017b} used those reconstructions for two of the systems, including HE0435 and RXJ1131, and then fitted a simply parametrized surface brightness profile to the reconstruction to mimic what is done in non-lensed AGN.

In this work, in order to reproduce more closely and uniformly what is
done in non-lensed AGN we develope a strategy to obtain a one step
measurement of the host galaxy light described by a \sersic surface
brightness profile. For the 4/8 systems already studied by the H0LiCOW
project, we will make a comparison to characterize systematic
uncertainties related to modelling techniques.

\subsection{Data Preparation and Modelling Setup}

We following the standard procedure as described by D20 to prepare the fitting ingredients including the lensing imaging data, noise level map and the PSF information. The imaging data are first drizzled to a higher resolution with a Gaussian kernel; the adopted resolution are listed in Table~\ref{data_set}. We then adopt the {\sc Photutils} by Python to model the global background light in 2-D based on SExtractor algorithm. We remove the background light and cut the clear image data into postage stamp at a suitable size. We draw the image mask for each systems to define the region in which the pixels would to be used to calculate the likelihood; see the top-left panel in each subplot in Figure~\ref{fig:image_inference}.

We carry out a forward modelling process to simultaneously constrain the lens model, subtract the central AGN light, and infer the photometry of the host galaxy. For any extended objects, including the lensing galaxy and source galaxy, we assume their surface brightness can be described by the 2-D elliptical \sersic\ profile. We start with a single \sersic\ profile and consider to use two \sersic\ if any significant residual indicate a multiply component. For a single \sersic\ profile, we set the prior of the \sersic\ index value $n$ between $[0.5-5.0]$ to avoid unphysical results\footnote{It has been studied in~\citet{Ding2017a} that choosing the prior for \sersic\ index $n$ yields unbiased host magnitude inferences.}. The bright nucleus is unresolved and modelled by a scaled point spread function (PSF) in the image plane. We also impose that the AGN and its host galaxy have the same center. Following standard practice that has show to produce good models \citep[e.g.,][and references therein]{Treu2010}, we adopt elliptical Power-law density profiles to define the surface mass density of the deflector, with an external shear.

We employ the imaging modelling tool \lenstronomy\footnote{\url{https://github.com/sibirrer/lenstronomy}}~\citep{lenstronomy} to perform the fitting task. Inspired by D20, we adopt a set of extensive modelling choices to perform the fitting for each system. We then apply a statistical measurement and perform a weighting algorithm to derive the final inference and estimate the uncertainty level, including the contribution of modelling choices. The modelling choices that we consider include the follows.
\begin{enumerate}
\item Following common practice, we select all the bright, isolated stars across the image frame of targets to define the PSF. Each selected star is considered as an initial PSF guess for the fit.
\item The central pixels of the AGNs are very bright and can be affected by large systematic errors during the interpolation of the subsampled PSF. To avoid overfitting the noise, we adopt two different modelling options: 1)~manually boost the noise estimate in the central area to effectively infinite ({\it noise boost}); 2)~perform the iterative PSF estimation as introduced by~\citet{Chen2016, Birrer2019} ({\it PSF iteration}).
\item To calculate the ray tracing under a higher resolution grid, we chose to oversample the model by a factor  $2\times2$ or $3\times3$ pixel$^{-1}$.
\item Using the lensing imaging alone is difficult to constrain the power-law slope. To mitigate the overfitting of the slope value, we repeat the fit for three values $[1.9, 2.0, 2.1]$ that are meant to bracket the range observed in lens galaxies \citep[e.g.,][]{Auger2010}.
\end{enumerate}
